% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Joseph Wetton}
\newcommand{\CVTitle}{Joseph Wetton's Resume}
\newcommand{\CVWebpage}{https://www.linkedin.com/in/joewetton/}

% PDF settings and properties.
\hypersetup{
	pdftitle={\CVTitle},
	pdfauthor={\CVAuthor},
	pdfsubject={\CVWebpage},
	pdfcreator={XeLaTeX},
	pdfproducer={},
	pdfkeywords={},
	unicode=true,
	bookmarks=true,
	bookmarksopen=true,
	pdfstartview=FitH,
	pdfpagelayout=OneColumn,
	pdfpagemode=UseOutlines,
	hidelinks,
	breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	\thispagestyle{empty}
	
	%%%%%%%%%%%%%%%
	% TITLE BLOCK %
	%%%%%%%%%%%%%%%
	
	\Title{\CVAuthor}
	
	\begin{SubTitle}
		\href{https://duckduckgo.com/?q=portland+Oregon+97201&ia=web&iaxm=maps}
		{Portland, Oregon 97201}
		\par
		\href{mailto:j@joewetton.com}
		{j@joewetton.com}
		\,\SubBulletSymbol\,
		+1\,(503)\,512‬-0704
		\,\SubBulletSymbol\,
		\href{\CVWebpage}
		{LinkedIn: JoeWetton}
	\end{SubTitle}
	
	\begin{Body}
		
		%%%%%%%%%%%%%%%
		%% SUMMARY %%
		%%%%%%%%%%%%%%%
		
		\Section
		{Summary}
		{Summary}
		{PDF:Summary}
		
		\Entry
		A college graduate with experience in programming, system design, and data analysis. Demonstrated ability to translate business problems into technical solutions and finally to implementation. Detail oriented with ability to communicate effectively in a team environment.
		
		
		
		%%%%%%%%%%%%%%%%%%%%%%%%%%%
		%% WORK EXPERIENCE %%
		%%%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\Section
		{Work\newline
			Experience}
		{Work Experience}
		{PDF:WorkExperience}
		
		\Entry
		\href{https://www.nike.com}
		{\textbf{Nike Inc.}},
		Beaverton, Oregon
		
		\BulletItem
		Software Engineer, Enterprise Finance Solutions
		\hfill
		\DatestampYMD{2018}{09}{15} --
		Present
		\begin{Detail}
			\SubBulletItem
			Conducted analysis, data modeling and made cloud architecture decisions to enable data flow between many systems.
			\SubBulletItem
			Developed CRUD REST API’s utilizing a serverless architecture, integrated by other teams within Nike to production.
			\SubBulletItem
			Created a continuous delivery pipeline for these API’s enabling sub-minute releases to AWS with zero downtime.
			\SubBulletItem
			Built test automation framework to execute during API deployments ensuring consistent functionality across releases.
			\SubBulletItem
			Integrated Okta Oauth Scope authorization to ensure utmost data and API endpoint security.
			\SubBulletItem
			Owned and developed an entire ETL (Extract, Transform, Load) pipeline and process to archive Nike's legacy finance file retention application. Involved identifying and extracting millions of accounts payable and receivable files spanning a decade from closed source proprietary system and uploading content into a modern API based digital asset management platform. Required analysis, solution design and execution.	\end{Detail}
		\Gap
		\Entry
		\href{https://www.truecar.com}
		{\textbf{TrueCar Inc.}},
		Santa Monica, California
		
		\BulletItem
		Software Engineering Intern, Post-Prospect User Experience Team
		\hfill
		\DatestampYMD{2017}{06}{15} --
		\DatestampYMD{2017}{12}{15}
		\begin{Detail}
			\SubBulletItem
			Wrote unit tests in Ruby for frontend and backend services, as part of a full stack team.
			\SubBulletItem
			Managed AWS infrastructure and continuous deployment practices.
			\SubBulletItem
			Built process for automated regression tests using Selenium web framework, MiniTest, Docker and Jenkins.
		\end{Detail}
		\Gap
		\Entry
		\href{http://intel.com}
		{\textbf{Intel Inc.}},
		Hillsboro, Oregon
		
		\BulletItem
		Software Engineering Intern, Silicon Validation Group
		\hfill
		\DatestampYMD{2016}{04}{15} --
		\DatestampYMD{2016}{09}{15}
		\begin{Detail}
			\SubBulletItem
			Wrote regression tests in Python using pytest framework used in Intel's silicon validation platform.
			\SubBulletItem
			Implemented Bullseye software to measure code coverage of silicon validation platform
			\SubBulletItem
			Optimized regression run times using synchronous nodes to execute runs reducing time to complete by up to 50\%.
		\end{Detail}
		
		\BulletItem
		\href{http://thunderbolttechnology.net}{Project Management Assistant, Thunderbolt Technology Group}
		\hfill
		\DatestampYMD{2014}{03}{15} --
		\DatestampYMD{2015}{08}{15}
		\begin{Detail}
			\SubBulletItem
			Managed Drupal powered marketing and engineering websites.
			\SubBulletItem
			Facilitated communication between Thunderbolt host/device product and Intel engineers via email and events.
			\SubBulletItem
			Created mobile web application to manage Thunderbolt Developer Conference (Plugfest)
		\end{Detail}
		\Gap
		
		\Entry
		\href{https://www.pdx.edu}
		{\textbf{Portland State University}},
		Portland, Oregon
		
		\BulletItem
		Teaching Assistant, Elements of Software Engineering
		\hfill
		\DatestampYMD{2017}{03}{15} --
		\DatestampYMD{2017}{06}{15}
		\begin{Detail}
			\SubBulletItem
			Assisted professor with class material which detailed the process of waterfall and agile methodologies for students new to software engineering and facilitated group student interactions.
		\end{Detail}
		
		
		%%%%%%%%%%%%%%%
		%% EDUCATION %%
		%%%%%%%%%%%%%%%
		
		\Section
		{Education}
		{Education}
		{PDF:Education}
		
		\Entry
		\href{https://www.pdx.edu}
		{\textbf{Portland State University}},
		Portland, Oregon
		
		\Gap
		\BulletItem
		B.S. in
		\href{https://www.pdx.edu/computer-science/}
		{Computer Science} \href{https://www.abet.org}{(ABET accredited)}
		\hfill
		\DatestampYMD{2013}{9}{15} --
		\DatestampYMD{2018}{06}{15}
		
		\Gap
		\BulletItem
		Lead Developer/Product Owner - Senior Project 
		\hfill
		\DatestampYMD{2018}{01}{15} --
		\DatestampYMD{2018}{06}{15}
		\begin{Detail}
			\SubBulletItem
			Product owner of id.ly - a cross platform mobile application, self-sovereign identification system and E2E encrypted messenger. 
			Developed by a collaboration of 7 students using an agile development style. Incorporated AES \& RSA encryption, Javascript, React Native, Jira \& Git.
			\SubBulletItem
			\href{https://github.com/bnelson777/id.ly}
			{Open Source: https://github.com/bnelson777/id.ly}
		\end{Detail}
		
		\Gap
		\BulletItem
		Java Group Project, Introduction to Performance Measurement
		\hfill
		\DatestampYMD{2017}{04}{15} --
		\DatestampYMD{2017}{06}{15}
		\begin{Detail}
			\SubBulletItem
			Designed with 2 other student peers a Java program to simulate bandwidth overhead of log packets over a local network between nodes running synchronously.
			\SubBulletItem
			Did statistical analysis on packet overhead measurements based on numerous traffic patterns.
		\end{Detail}
		
		
		
		%%%%%%%%%%%%%%%%%%%%%%%%%
		%% SKILLS %%
		%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\Section
		{Skills}
		{Skills}
		{PDF:Skills}
		
		\Entry
		\textbf{Expert:}
		Python, Java, C++, Ruby, MySQL, HTML, CSS, PHP
		\Entry
		\textbf{Intermediate:}
		C, AWS, Javascript (React/React Native/Node), Elasticsearch, Git
		\Entry
		\textbf{Basic:}
		Swift, Objective-C, C\#, Haskell, MS-DOS, Docker
		%%%%%%%%%%%%%%%%%%%%%%%%%
		%% ACTIVITIES %%
		%%%%%%%%%%%%%%%%%%%%%%%%%
		
		\Section
		{Awards}
		{Awards}
		{PDF:Awards}
		\Entry
\textbf{JDI: Just Do It Award Nominee 2020:}
Recognition of excellence and commitment to Nike’s maxims.
\Entry
\textbf{1st Place Innovation Challenge:}
VersionOne Scanner Mobile App built in React Native that allows bulk updating of agile stories. The app utilized the phones camera and scans QR code’s on stories on boards.
\Entry
\textbf{Judges Award Innovation Challenge:}
Slackbot that allows Nike Employees to get notified when a shoe goes up for sale in their size. Utilizes AWS Lambda/API Gateway/DynamoDB \& Slack API.
		%\Gap
		%\BulletItem
		%Java Group Project, Introduction to Performance Measurement
		
		%%%%%%%%%%%%%%%%%%
		%% PUBLICATIONS %%
		%%%%%%%%%%%%%%%%%%
		
		
		
		
		
	\end{Body}
	
	%%%%%%%%%%%
	% CV NOTE %
	%%%%%%%%%%%
	
	%\UseNoteFont%
	%\null\hfill%
	%[\textit{\CVNote}]
	\clearpage
	\thispagestyle{empty}
	
\end{document}
